# Reproducible Research : Project 1

## Loading and preprocessing the data
```{r}
data1 <- read.csv("activity.csv")
```

## What is mean total number of steps taken per day?
```{r}
totalsteps <- tapply(data1$steps,data1$date,FUN=sum, na.rm=TRUE)
library(ggplot2)
qplot(totalsteps,binwidth=1000,xlab="Total number of steps per day")
mean(totalsteps,na.rm = TRUE)
median(totalsteps, na.rm = TRUE)
```

## What is the average daily activity pattern?
### Plotting a time series chart per 5-minute interval
```{r}
avgsteps <- aggregate(x=list(steps=data1$steps),by=list(interval=data1$interval),FUN=mean,na.rm=TRUE)
ggplot(data=avgsteps,aes(x=interval,y=steps)) + geom_line() + 
  xlab("5-minute interval") + ylab("Average steps")
```

## Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?
```{r}
avgsteps[which.max(avgsteps$steps),]
```

## Imputing missing values
### replace missing value by the mean of its 5-minute interval
```{r}
imputevalue <- function(steps, interval) {
  filled <- NA
  if (!is.na(steps))
    filled <- c(steps)
  else
    filled <- (avgsteps[avgsteps$interval==interval, "steps"])
  return(filled)
  
}
impute <- data1
impute$steps <- mapply(imputevalue, impute$steps, impute$interval)
```

## plotting histogram of imputed dataset
```{r}
Totalsteps <- tapply(impute$steps, impute$date, FUN=sum)
qplot(Totalsteps, binwidth=1000, xlab="total number of steps taken each day")
```

## mean and media values of imputed dataset
```{r}
mean(Totalsteps)
median(Totalsteps)
```
## Are there differences in activity patterns between weekdays and weekends?
```{r}
week <- function(date) {
    day <- weekdays(date)
    if (day %in% c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday"))
        return("weekday")
    else if (day %in% c("Saturday", "Sunday"))
        return("weekend")
    else
        stop("date error")
}
impute$date <- as.Date(impute$date)
impute$day <- sapply(impute$date, FUN=week)
```
## panel plot containing plots of average number of steps taken on weekdays and weekends.
```{r}
averages <- aggregate(steps ~ interval + day, data=impute, mean)
ggplot(averages, aes(interval, steps)) + geom_line() + facet_grid(day ~ .) +
    xlab("5-minute interval") + ylab("Number of steps")
```
